\documentclass[utf8,a4paper]{ctexart}
\setCJKmainfont[ItalicFont={KaiTi},BoldFont={SimHei}]{SimSun}
\setCJKsansfont{SimHei}
\setCJKmonofont{FangSong}
\usepackage{graphicx}
\usepackage[top=30mm,left=3.0cm,bottom=2.5cm,right=2.5cm]{geometry}

\usepackage{listings}	源代码
\usepackage{booktabs}

% Title Page
\title{Experiment Report of Computer Architecture}
\author{Lei Zungjyun 李颂元 21321293 Anqing-Zhao 赵安清 21321047}

\begin{document}
\maketitle

\section{Topic}
[5] Build a New Linux Kernel Image(3.12) for ARM ISA in gem5 FS Mode.

\section{Introduce}
	\subsection{Steps}
		\begin{enumerate}
			\item
			Install requisite packages.
			\item
			Download gem5 and compile it for ARM (gem5.opt).
			\item
			Download Linux kernel and cross-compile it for ARM.
			\item
			Configur M5\_DIR (vmlinux-3.12, linux-arm-ael.img).
			\item
			Run and test (m5term).
		\end{enumerate}
		
	\subsection{Hardware}
	We use a computer in lab to compile Linux and run gem5 for testing new-version Linux. The machine's performance is a bit low, so it brings some trouble to us.
		\begin{enumerate}
			\item
			Device: Optiplex GX620.
			\item
			OS: Ubuntu 13.04.
		\end{enumerate}

\section{Obstacles}
	\subsection{Compile Errors}
	Some compile errors as following.
		\subsubsection{gem5}
			\begin{enumerate}
				\item
				Inadequate DRAM.
				\item
				scons build/ARM/gem5.opt -j2.
			\end{enumerate}
		\subsubsection{Kernel}
			\begin{enumerate}
				\item
				make ARCH=arm O=PATH menuconfig.
				\item
				make ARCH=arm CROSS\_COMPILE=arm-linux-gnueabi-O=PATH vmlinux-3.12.
				\item
				Prerequisite.
			\end{enumerate}
			
	\subsection{Runtime Errors}
	Some runtime errors as following.
		\subsubsection{gem5}
			\begin{enumerate}
				\item
				SE mode runs smoothly.
			\end{enumerate}
		\subsubsection{Kernel}
			\begin{enumerate}
				\item
				–mem-size.
				\item
				–kernel.
				\item
				–disk-image.		
			\end{enumerate}

\section{Solution}
We have no much experience in compiling a new-version Linux for ARM. During studying and trying, we countered various problem and wierd situation. To find answer, effective methods used as following.
	\begin{enumerate}
		\item
		Classification: Tutorials.
		\item
		Index: Google.
		\item
		Compromise: Documentation and videos.
	\end{enumerate}
	
\section{Cooperation}
This topic is hardly divide-and-conquering. we discuss and solve the problem together and get the ideal result eventually.

\end{document}